Fractional anisotropy as a tracer of cosmic voids

### 2014-12-19 cosmic_voids.tex
revisados los 5 primeros parrafos de la introduccion

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81,  Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe, based on gravitational instabilities in primordial 
stages and leaded by the seminal work of \citet{Zeldovich70}, are 
consistent with the Cosmic Web picture, where planar pancake-like regions 
of matter enclose enormous underdense voids and are bordered, in turn, by 
thin filaments and high-density clumpy knots \citep{Bond96}. First 
theoretical models for describing formation, dynamics and properties of 
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were 
dramatically complemented and extended by first numerical studies based 
on simulations \citep{Martel90, Regos91, Weygaert93, Dubinski93}. This 
tendency of using numerical data from N-body simulations, fuelled by last 
generation computing systems and ever more efficient numerical algorithms, 
has become increasingly common in the last years as a powerful analysis 
toolkit of cosmic voids (for an extensive compilation of previous 
numerical works, see \citet{Colberg08}).

At present, studying voids may be considered as a threefold enterprise
\citep{Platen07}: first, they are a key ingredient of the Cosmic Web as 
they dominate almost the entire volume distribution at large-scales and 
additionally, they compensate overdense structures in the total budget of 
matter. This implies that a full understanding of their evolution and 
properties is essential for fathoming the high complexity of the Cosmic 
Web. Second, they provide a valuable resource for inferring and probing 
cosmological parameters as their structure and dynamics are highly 
determined by these values. Third, they constitute an unique and still 
largely pristine environment in which can be tested galaxy evolution.

Although a visual recognition of voids in galaxy surveys and simulations
is possible in most cases, a formal systematic identification is necessary 
for statistically meaningful studies. However, a basic yet essential issue 
remains regarding the definition itself of what a void is. There is not a 
general consensus about an unambiguous definition of cosmic voids and 
therefore, there can be found many different void finding techniques 
throughout the literature (for a detailed comparison of different schemes, 
see the Void Finder Comparison Project \citet{Colberg08}). In spite of the 
diversity of existing schemes, they can be roughly classified into two 
main types: first, geometric schemes based on point spatial or redshift 
distribution of galaxies in surveys or catalogues of dark matter halos in 
simulations \citep{Kauffmann91, Muller00, Gottlober03, Hoyle04, Brunino07, 
Foster09, Micheletti14, Sutter14}, and second, schemes based on the smooth 
and continuous matter density field either from simulations or from 
reconstruction procedures on surveys \citep{Plionis02, Colberg05, 
Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}.

Here we introduce a new tracer of the structure of cosmic voids built from 
two tensorial web schemes, i.e. the Tweb, based on the Hessian of the 
gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
Vweb, based on the velocity shear tensor \citep{Hoffman12}. These web 
schemes classify the Cosmic Web into four different types of environment
depending on the counting of the number of eigenvalues below an 
user-defined threshold ($\lambda_{th}$), namely voids (3 eigenvalues below
$\lambda_{th}$), sheets (2), filaments (1) and knots or clusters (0).
The tidal and the shear tensors have proven to be more fundamental than 
the density field as they also trace the collapsing or expanding nature of 
the matter field, which ultimately is what defines the underlying dynamics 
of the Cosmic Web. Furthermore, the density field is degenerated regarding 
the defined types of environment \citep{Hahn07}, which implies that is not 
possible to assign a priori a range of density values to each of them. 
This yields that the usually adopted definition of voids as simply 
underdense regions in the large-scale matter distribution, is not precise 
enough as it excludes a proper description of the internal structure of 
voids.

>>>>

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

On the theoretical side the rough theoretical framework that explains
the origin of voids was stablished in the seminal work of
\citet{Zeldovich70} and refined in the following decades.  
The first detailed theoretical models describing formation, dynamics
and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
  Blumenthal92} were  complemented and extended by numerical studies
\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
Currently, the dominant tendency to study voids relies on using data
from N-body simulations. For an extensive compilation of previous 
numerical works we refer the reader to \citet{Colberg08}.

The relevance of voids to cosmological studies can be summarized in
three aspects \citep{Platen07}. 
First, voids are a key ingredient of the Cosmic Web. 
They dominate the volume distribution at large-scales and
additionally, they compensate overdense structures in the total budget
of  matter.  
Second, voids provide a valuable resource for inferring and probing 
cosmological parameters as their structure and dynamics are highly 
determined by these values. 
Third, they are a  largely a largely pristine environment to test
galaxy evolution.

Although a visual recognition of voids in galaxy surveys and simulations
is possible in most cases, a formal systematic identification is desirable
for statistical studies. 
However, the community does not have an unambiguous definition of cosmic
voids. 
There are nany different void finding techniques in the literature
(for a detailed comparison of different schemes,  see the Void Finder
Comparison Project \citet{Colberg08}). 
In spite of the diversity of existing schemes, they can be roughly
classified into two main types. First, geometric schemes based on
point spatial or redshift  distribution of galaxies in surveys or dark
matter halos in  simulations \citep{Kauffmann91, Muller00,
  Gottlober03, Hoyle04, Brunino07,  Foster09, Micheletti14, Sutter14};
second, schemes based on the smooth  and continuous matter density
field either from simulations or from  reconstruction procedures on
surveys \citep{Plionis02, Colberg05,  Shandarin06, Platen07,
  Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}.

Here we introduce a new tracer of the structure of cosmic voids that
can be used once the continous matter density or velocity distribution
is known. 
The algorithm is based on two tensorial schemes used to classify the
cosmic web. 
The first (the T-web) is based on the Hessian of the gravitational potential or
tidal tensor \citep{Hahn07, Forero09}. 
The second (the V-web) is based on the velocity shear tensor
\citep{Hoffman12}. 
These web schemes classify the Cosmic Web into four different types of
environment depending on the counting of the number of eigenvalues below an 
user-defined threshold ($\lambda_{rm th}$): voids, sheets, filaments and
knots for $3,2,1$ or $0$ eigenvalues below $\lambda_{\rm th}$, respectively.

%%

The tidal and the shear tensors have proven to be more fundamental than 
the density field as they also trace the collapsing or expanding nature of 
the matter field, which ultimately is what defines the underlying dynamics 
of the Cosmic Web. Furthermore, the density field is degenerated regarding 
the defined types of environment \citep{Hahn07}, which implies that is not 
possible to assign a priori a range of density values to each of them. 
This yields that the usually adopted definition of voids as simply 
underdense regions in the large-scale matter distribution, is not precise 
enough as it excludes a proper description of the internal structure of 
voids.
